---
title: "documentation ap"
author: "Aurelien Roussille"
date: "25 décembre 2017"
output: html_document
runtime: shiny
---

#app to analyse french main stock market

##Summary

Here, we load the main stock from the french market CAC 40, and the index itself, to observe it. A tool is added, it a simple moving average, at 2, 5 and 10 days, to get the differents trends.

How to use it ?


First, select the stock (the index itself is selected by default), then, with the graph load with plotly, you can observe the evolution of the stock, via a candlestick graph. 


```{r input, echo=FALSE}
comp<-c("CAC40","Total","Sanofi","BNP","LVMH","Airbus","Axa","L'Oreal","Air Liquide","Danone","Vinci","Schneider","Societe Generale","Kering","Orange")
ref<-data.frame("^FCHI","FP.PA","SAN.PA","BNP.PA","MC.PA","AIR.PA","CS.PA","OR.PA","AI.PA","BN.PA","DG.PA","SU.PA","GLE.PA","KER.PA","ORA.PA")
colnames(ref)<-comp

      selectInput("titre","Company:",
                  choice=colnames(ref))
      checkboxInput("Sma","Simple Moving Average",FALSE)

```

The green is a day where the stock increased and red it decreased. You can zoom etc... as plotly permit you to do it.


```{r echo=FALSE}
suppressMessages(suppressWarnings(library(quantmod)))
suppressMessages(suppressWarnings(library(plotly)))
suppressMessages(suppressWarnings(library(dplyr)))

data<-read.csv("stock.csv",sep=",",dec=".",header=TRUE)
data<-data[,-1]

sortie<-reactive({
    compa<-input$titre
    temp<-filter(data,name==compa)
  
   
    if (input$Sma==TRUE){
      sma1<-rollmean(temp$Close,2)
      sma5<-rollmean(temp$Close,5)
      sma10<-rollmean(temp$Close,10)
      temp$Date<-as.Date(temp$Date)
      temps<-subset(temp,Date>="2017-09-25")
      temp<-cbind(temps,tail(sma1,dim(temps)[1]),tail(sma5,dim(temps)[1]),tail(sma10,dim(temps)[1]))
      colnames(temp)<-c("Date","Open","High","Low","Close","Volume","Adjusted","name","sma1","sma5","sma10")
      temp
    } else {
      temp$Date<-as.Date(temp$Date)
      temps<-subset(temp,Date>="2017-09-25")
      temp<-temps
      temp
    }
  })
  
 renderPlotly({
    sortie<-sortie()
    if (input$Sma==FALSE){
      plot_ly(sortie,x=~Date,type="candlestick",
              open=~Open,close=~Close,high=~High,low=~Low)%>%
        layout(title="Quarterly evolution")
    } else {
      plot_ly(sortie,x=~Date,type="candlestick",
              open=~Open,close=~Close,high=~High,low=~Low)%>%
        layout(title="Quarterly evolution")%>%
        add_lines(y=~sma1,name="2 day")%>%
        add_lines(y=~sma5,name="5 days")%>%
        add_lines(y=~sma10,name="10 days")
    }
    
    
  })
  
```